---
title: "Praise Adult Analysis"
author: "Mika Asaba (masaba@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_float: true
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

Load Relevant Libraries and Functions
-------------------------------------------------
```{r, echo=FALSE, include=F}
rm(list=ls())
library(tidyr)
library(dplyr)
library(ggplot2)
library(langcog) 
library(rjson) #reading in JSON files
library(lme4) 
library(psych)
library(R.matlab) #reading in MATLAB files
library(readr)
library(ggthemes)
library(here)
theme_set(theme_few())
```


**Muliplot function.**
```{r,echo=FALSE}
#combining multiple graphs into one
#example: multiplot(name_graph1, name_graph2)

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

Experiment 1
------------------------------------------------
### Read in data
```{r, echo=FALSE}
path <- "/Users/masaba/Dropbox/Research/UP_mTurk/"
files <- dir(paste0(path,"data/rd1/"), 
             pattern = "*.json")

data.raw <- data.frame() #for practice data
demog.raw <- data.frame()

for (f in files) {
  jf <- paste0(path, "data/rd1/",f)
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  #data frame for identity data
  data <- data.frame(workerid = factor(jd$WorkerId),
                     warmup = factor(jd$answers$data$warmup_response[[1]][[1]]$value),
                     teachername1 = factor(jd$answers$data$teacher_order[1]),
                     teachername2 = factor(jd$answers$data$teacher_order[2]),
                     teachertype1 = factor(jd$answers$data$trial_order[1]),
                     teachertype2 = factor(jd$answers$data$trial_order[2]),
                     memcheck1 = factor(jd$answers$data$memcheck_response[[1]][[1]]$value),
                     memcheck2 = factor(jd$answers$data$memcheck_response[[2]][[1]]$value),
                     tracing = factor(jd$answers$data$tracing_response[[1]][[1]]$value),
                     nicer = factor(jd$answers$data$nicer_response[[1]][[1]]$value),
                     explanation = factor(jd$answers$data$explanation),
                     age = factor(jd$answer$data$demographics[[1]][[1]]$value),
                     lang = factor(jd$answer$data$demographics[[1]][[2]]$value),
                     race = factor(jd$answer$data$demographics[[1]][[3]]$value),
                     gender = factor(jd$answer$data$demographics[[1]][[4]]$value),
                     browser = factor(jd$answer$data$demographics[[1]][[5]]$value),
                     issues = factor(jd$answer$data$demographics[[1]][[6]]$value))
  
  data.raw <- bind_rows(data.raw,data)
}
```

### Data preprocessing
```{r}
data.pre <- data.raw %>%
  transmute(id = workerid,
            age = age,
            lang = lang,
            gender = gender,
         warmupcheck = warmup == "A",
         sp = ifelse(teachertype1 == "SP", teachername1, teachername2),
         op = ifelse(teachertype1 == "OP", teachername1, teachername2),
         tracing = ifelse(tracing == "Jane_tracing", "Jane", "Susan"),
         tracing_choice = ifelse(tracing == sp, "Contingent Praise Teacher", "Overpraise Teacher"),
         tracing_choseContingent = tracing_choice == "Contingent Praise Teacher",
         nicer_choice = ifelse(nicer == sp, "Contingent Praise Teacher", "Overpraise Teacher"),
         memcheck_sp = ifelse(teachertype1 == "SP", memcheck1 == 3, memcheck2 == 3),
         memcheck_op = ifelse(teachertype1 == "OP", memcheck1 == 6, memcheck2 == 6),
         explanation = explanation)
```

### Exclude subjects
**Remove subjects who failed warmup evaluation question, or either memory check.**
```{r}
data.fin <- data.pre %>%
  filter(warmupcheck == TRUE,
         memcheck_sp == TRUE,
         memcheck_op == TRUE)

data.ex.warmup <- data.pre %>%
  filter(warmupcheck == FALSE)

#4 failed the warm up check question

data.ex.memsp <- data.pre %>%
  filter(memcheck_sp == FALSE)

data.ex.memop <- data.pre %>%
  filter(memcheck_op == FALSE)
```

### Demographics
```{r}
age.table <- data.fin %>%
  ungroup() %>%
  summarise(n = n(),
            mean.age = mean(as.numeric(age)),
            sd.age = sd(as.numeric(age)),
            min.age = min(as.numeric(age)),
            max.age = max(as.numeric(age)))

age.table

gender.table = table(data.fin$gender)

gender.table
```
Subjects were recruited from Amazon Mechanical Turk (N = `r age.table$n`, M(SD) = `r age.table$mean.age`(`r age.table$sd.age`), Range = `r min.age` - `r max.age`). Subjects were excluded for failing to pass the memory check questions (N = X).

### Tables 

**Tracing question: Kristen wants to enter one of these tracings into a contest. Which tracing should she bring?**
```{r}
tracing.table = data.fin %>%
  group_by(tracing_choice) %>%
  rename(choice = tracing_choice) %>%
  summarise(n = n()) %>%
  mutate(question = "Which tracing?",
         freq = n / sum(n),
         SE = sqrt(freq*(1-freq)/sum(n)), #standard error
         E = qnorm(.975)*SE, #margin of error
         low_95 = freq - E,
         upp_95 = freq + E)

tracing.table
```

**Niceness question: Who is nicer?**
```{r}
nicer.table = data.fin %>%
  group_by(nicer_choice) %>%
  rename(choice = nicer_choice) %>%
  summarise(n = n()) %>%
  mutate(question = "Who is nicer?",
         freq = n / sum(n),
         SE = sqrt(freq*(1-freq)/sum(n)), #standard error
         E = qnorm(.975)*SE, #margin of error
         low_95 = freq - E,
         upp_95 = freq + E)

nicer.table

data.table = full_join(nicer.table, tracing.table)
data.table

data.table.ci = filter(data.table, choice == "Overpraise Teacher")
data.table.ci
```

### Plots
```{r}
tracing.nicer.plot = ggplot(data.table, aes(question, freq, fill=choice)) +
    geom_bar(stat="identity",position="fill",width=.5)+
  ylab("Proportion of Choices")+
  theme_minimal() +
    theme(text = element_text(size=20),
          axis.title.x=element_blank()) +
  guides(fill=guide_legend(title="Choice"))+
  scale_fill_manual(values=c("indianred","steelblue")) +
  geom_linerange(data = data.table.ci, mapping=aes(x=question, ymin = low_95, ymax=upp_95))+
  geom_hline(yintercept=.5, linetype="dotted")
  
tracing.nicer.plot
```

### Analyses
**Binomial tests.**
```{r}
#Tracing question: Do subjects choose the Selective Praise Teacher's tracing above chance? 
binom.test(tracing.table$n[1], tracing.table$n[1] + tracing.table$n[2])

#Niceness question: Do subjects choose the Overpraise Teacher as nicer above chance?
binom.test(nicer.table$n[1], nicer.table$n[1] + nicer.table$n[2])
```

**Chi-squared tests.**
```{r}
#Is there a difference between subject's choices in the Tracing vs. Niceness question?
chisq.test(matrix(c(tracing.table$n[1], tracing.table$n[2], nicer.table$n[1], nicer.table$n[2]), ncol=2))
```

Experiment 2
------------------------------------------------
**The only difference between Experiment 1 and Experiment 2 is the niceness question. In Experiment 2, we ask specifically about the goal of the teacher (``One of these teachers wanted to be nice. Who was trying to be nice?''), whereas in Experiment 1, we asked about the which teacher the subject herself thought was nicer.** 

### Read in data
```{r}
path <- "/Users/masaba/Dropbox/Research/UP_mTurk/"
files <- dir(paste0(path,"data/rd2"), 
             pattern = "*.json")

data2.raw <- data.frame() #for practice data

for (f in files) {
  jf <- paste0(path, "data/rd2/",f)
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  
  #data frame for identity data
  data2 <- data.frame(workerid = factor(jd$WorkerId),
                     warmup = factor(jd$answers$data$warmup_response[[1]][[1]]$value),
                     teachername1 = factor(jd$answers$data$teacher_order[1]),
                     teachername2 = factor(jd$answers$data$teacher_order[2]),
                     teachertype1 = factor(jd$answers$data$trial_order[1]),
                     teachertype2 = factor(jd$answers$data$trial_order[2]),
                     memcheck1 = factor(jd$answers$data$memcheck_response[[1]][[1]]$value),
                     memcheck2 = factor(jd$answers$data$memcheck_response[[2]][[1]]$value),
                     tracing = factor(jd$answers$data$tracing_response[[1]][[1]]$value),
                     nicer = factor(jd$answers$data$nicer_response[[1]][[1]]$value),
                     explanation = factor(jd$answers$data$explanation),
                     age = factor(jd$answer$data$demographics[[1]][[1]]$value),
                     lang = factor(jd$answer$data$demographics[[1]][[2]]$value),
                     race = factor(jd$answer$data$demographics[[1]][[3]]$value),
                     gender = factor(jd$answer$data$demographics[[1]][[4]]$value),
                     browser = factor(jd$answer$data$demographics[[1]][[5]]$value),
                     issues = factor(jd$answer$data$demographics[[1]][[6]]$value))
  
  data2.raw <- bind_rows(data2.raw,data2)
}

```

### Data preprocessing
```{r}
data2.pre <- data2.raw %>%
  transmute(id = workerid,
            age = age,
            lang = lang,
            gender = gender,
         warmupcheck = warmup == "A",
         sp = ifelse(teachertype1 == "SP", teachername1, teachername2),
         op = ifelse(teachertype1 == "OP", teachername1, teachername2),
         tracing = ifelse(tracing == "Jane_tracing", "Jane", "Susan"),
         tracing_choice = ifelse(tracing == sp, "Contingent Praise Teacher", "Overpraise Teacher"),
         tracing_choseContingent = tracing_choice == "Contingent Praise Teacher",
         nicer_choice = ifelse(nicer == sp, "Contingent Praise Teacher", "Overpraise Teacher"),
         nicer_choseContingent = nicer_choice == "Contingent Praise Teacher",
          memcheck_sp = ifelse(teachertype1 == "SP", memcheck1 == 3, memcheck2 == 3),
         memcheck_op = ifelse(teachertype1 == "OP", memcheck1 == 6, memcheck2 == 6),
         explanation = explanation,
         condition = "sp/op")
```

### Exclude subjects
**Remove subjects who failed warmup evaluation question, or either memory check.**
```{r}
data2.fin <- data2.pre %>%
  filter(warmupcheck == TRUE,
         memcheck_sp == TRUE,
         memcheck_op == TRUE)

data2.ex.warmup <- data2.pre %>%
  filter(warmupcheck == FALSE)

#4 failed the warm up check question

data2.ex.memsp <- data2.pre %>%
  filter(memcheck_sp == FALSE)

data2.ex.memop <- data2.pre %>%
  filter(memcheck_op == FALSE)
```

### Demographics
```{r}
age2.table <- data2.fin %>%
  ungroup() %>%
  summarise(n = n(),
            mean.age = mean(as.numeric(age)),
            sd.age = sd(as.numeric(age)),
            min.age = min(as.numeric(age)),
            max.age = max(as.numeric(age)))

age2.table

gender2.table = table(data2.fin$gender)
gender2.table
```

### Tables 

**Tracing question: Kristen wants to enter one of these tracings into a contest. Which tracing should she bring?**
```{r}
tracing2.table = data2.fin %>%
  group_by(tracing_choice) %>%
  rename(choice = tracing_choice) %>%
  summarise(n = n()) %>%
  mutate(question = "Which tracing?",
         freq = n / sum(n),
         SE = sqrt(freq*(1-freq)/sum(n)), #standard error
         E = qnorm(.975)*SE, #margin of error
         low_95 = freq - E,
         upp_95 = freq + E)

tracing2.table

tracing.adult <- data2.fin %>%
#  mutate(tracing_selective = as.numeric(tracing_selective))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "tracing_choseContingent")

tracing.adult
```

**Niceness question: Who is nicer?**
```{r}
nicer2.table = data2.fin %>%
  group_by(nicer_choice) %>%
  rename(choice = nicer_choice) %>%
  summarise(n = n()) %>%
  mutate(question = "Who wanted to be nice?",
         freq = n / sum(n),
         SE = sqrt(freq*(1-freq)/sum(n)), #standard error
         E = qnorm(.975)*SE, #margin of error
         low_95 = freq - E,
         upp_95 = freq + E)

nicer2.table

data2.table = full_join(nicer2.table, tracing2.table)

data2.table.ci = filter(data2.table, choice == "Overpraise Teacher")
data2.table.ci

nicer <- data2.fin %>%
#  mutate(tracing_selective = as.numeric(tracing_selective))%>%
  group_by(condition) %>%
  multi_boot_standard(col = "tracing_choseContingent")

tracing
```

### Plots
```{r}
tracing2.nicer.plot = ggplot(data2.table, aes(question, freq, fill=choice)) +
    geom_bar(stat="identity",position="fill",width=.5)+
  ylab("Proportion of Choices")+
  theme_minimal() +
    theme(text = element_text(size=20),
          axis.title.x=element_blank()) +
  guides(fill=guide_legend(title="Choice"))+
    scale_fill_manual(values=c("indianred","steelblue")) +
  geom_linerange(data = data2.table.ci, mapping=aes(x=question, ymin = low_95, ymax=upp_95))+
  geom_hline(yintercept=.5, linetype="dotted")
  
tracing2.nicer.plot
```

### Analyses
**Binomial tests.**
```{r}
#Tracing question: Do subjects choose the Selective Praise Teacher's tracing above chance? 
binom.test(tracing2.table$n[1], tracing2.table$n[1] + tracing2.table$n[2])

#Niceness question: Do subjects choose the Overpraise Teacher as nicer above chance?
binom.test(nicer2.table$n[1], nicer2.table$n[1] + nicer2.table$n[2])
```

**Chi-squared tests.**
```{r}
#Is there a difference between subject's choices in the Tracing vs. Niceness question?
chisq.test(matrix(c(tracing2.table$n[1], tracing2.table$n[2], nicer2.table$n[1], nicer2.table$n[2]), ncol=2))
```

Experiment 1 and Experiment 2
--------------------------------------------------
```{r}
multiplot(tracing.nicer.plot, tracing2.nicer.plot) #both plots together
```
