---
title: "Did I really do well? Young children are sensitive to the informativeness of others' praise and use it to evaluate their own work"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"
author-information: >
    \author{{\large \bf Mika Asaba},  {\large \bf Emily Hembacher}, {\large \bf Helen Qiu},
    {\large \bf Brett Anderson}, {\large \bf Michael Frank}, {\large \bf Hyowon Gweon}
    \\ Department of Psychology, Stanford University}
abstract: 
    "Young children constantly receive praise about their abilities, skills, and products. While much work has been devoted to how praise influences children's motivation and self-esteem, an open question is how children evaluate praise from others and use it to assess their own work. Given young children's ability to track informant's accuracy and selectively trust those who are more reliable, we examine their ability to monitor the informativeness of others' praise. In particular, this work investigates whether young children weight evaluations from a teacher who provides praise with respect to the quality of a piece of work higher than evaluations from a teacher who always provide praise. We show that a dults (Experiment 1) and even 4-5 year-olds (Experiment 2) show sensitivity to the difference in informativeness between these two teachers, even when controlling for the frequency of praise (Experiment 3). These findings provide evidence that from a young age, children can selectively use others' praise to evaluate their own work."
keywords:
    "praise, theory of mind, uncertainty"
    
output: cogsci2016::cogsci_paper
editor_options: 
  chunk_output_type: console
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)
library(langcog)
library(lme4)
library(stringr)
library(magrittr)
library(viridis)
```

```{r,echo=FALSE}
#combining multiple graphs into one
#example: multiplot(name_graph1, name_graph2)

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

Imagine that you just gave a presentation and you are uncertain of how well you did, so you ask your friends, Tim and Sam, for their opinions. While Tim usually provides positive feedback to everyone regardless of how well they actually performed, Sam tends to provide more helpful, honest feedback. Given these different patterns of evaluations, you might use Sam's evaluation to actually learn about the quality of your presentation. As adults, we intuitively understand that others' feedback can be differentially informative depending on the evaluator's expertise, commmunicative goal, or sincerity, and we can take these factors into consideration when interpreting others' evaluations of us. These abilities might be especially critical for young children, as they are attempting to learn about their skills, abilities, and weaknesses amidst a flood of constant feedback and evaluations from others. 

In particular, performance praise -- positive evaluations of a person's performances or attributes [see @kanouse1981semantics] -- has become ubiquitous in parenting and education practices in Western societies. Given that children's intrinsic motivation is differentially influenced depending on whether praise received inflated or not [@brummelman2014s], or whether it is directed at an inherent ability or effort [@kamins1999person], it seems that children can at least differentiate between different types of praise. Can children also reason about the informational value of others' praise? In the current work, we investigate (1) whether young children can reason about the \textit{informativeness} of others' praise, or the reliable contingency of praise on the quality of a product, from others' history of providing praise, and (2) if so, whether they can use others' informativeness to assess their own work.

<!-- In particular, performance praise -- positive evaluations of a person's performances or attributes [see @kanouse1981semantics] -- has become ubiquitous in parenting and education practices in Western societies. Given that children's intrinsic motivation can be differentially influenced depending on whether it is inflated or not [@brummelman2014s], or whether it is directed at an inherent ability or effort [@kamins1999person], it seems that children can differentiate between different types of praise.  -->



<!-- However, while much work has been devoted to how praise influences children's self-esteem [e.g., @brummelman2014s], intrinsic motivation [see @henderlong2002effects for a review], and learning behaviors [e.g., @mueller1998praise], one open question is how young children might monitor the \textit{informativeness} of praise and selectively use others' praise to assess their own work. -->


<!-- In the current work, we examine whether young children share these intuitions, in particular whether they can (1) track the informativeness of others' praise from prior observations and (2) how they use might others' informativeness to appropriately evaluate their own work. -->


<!-- In order to make appropriate inferences about their abilities and products, children must learn to figure out when praise is meaningful and when it should be discounted. Here, we examine children's sensitivity to the \textit{informativeness} of praise and if so, whether children are strategic in how they use praise to assess their own work. -->

<!-- One of the challenges of childhood is learning about one's abilities, traits, skills, and weaknesses. There are many ways in which children can learn about themselves (e.g., observing their successes and failures, comparing themselves to others), but one important source of information is \textit{others' evaluations} of who they are ("You are so smart!") and what they can do ("You are great at tracing!"). However, young children are constantly flooded with social information about the self, and it might be difficult for them to determine which sources of information are meaningful and which should be discounted. -->

<!-- Performance praise -- positive evaluations of a person's performances or attributes [see @kanouse1981semantics] -- has become ubiquitous in parenting and education practices in Western societies. How do children reason about and evaluate others' praise for them?  -->


<!-- For instance, imagine that you are learning how to make cookies. You make two batches of cookies and ask two of your friends, Anne and Sally, what they think. Anne always says that anyone's cookies are good, even if they are not very tasty. On the other hand, Sally provides more helpful, honest feedback and only says that the cookies are good when they are actually good. So, Anne tries one type of cookie and says that it is great; Sally tries the other type of cookie and also says that it is great. Although both friends provided the same praise for each cookie, you might be more certain about Sally's evaluation and infer that that batch of cookies is better. In the current work, we examine whether young children can track the informativeness of others' praise from prior observations and how they use might others' informativeness to appropriately evaluate their own work.  -->

<!-- Some prior work has argued that children may perceive praise as insincere when it is overly general or inconsistent with how the child views herself, especially when the child can think of counterexamples to the evaluation [see @henderlong2002effects]. While the consistency between the child's and informant's evaluation of a product the child created could provide cues to sincerity, children can also observe whether the contingency of an informant's praise on quality to determine who to trust for evaluative information. -->

<!-- Main question + children's sensitivity to sincerity -->

<!-- Selective trust -->

<!-- Our main prediction is that young children can monitor others' the informativeness of others' praise and use it to effectively learn about their own abilities and products.  -->

When faced between a teacher who always provides praise and one who selectively provides praise, contingent on the quality of a product, one possibility is that children can differentiate between the teachers and trust the informant who provides selective praise. Indeed, much work on children's evaluations of others' testimony has shown that young children appear to be quite savvy in figuring out \textit{whose} information to trust, at least when it comes to information about the physical world (e.g., the names or locations of objects, or how a toy works). By the preschool years, children can track the accuracy of others' testimony (e.g., whether they provide correct or incorrect labels of common household objects), prefer to learn from those who previously provided accurate labels [@koenig2004trust, @birch2008three, @harris2011young], and can continually update their evaluations of others' trustworthiness across multiple interactions [@ronfard2017preschoolers]. 

Children are not only able to make evaluations based on the accuracy of others' verbal testimony, but also the informativeness of others' pedagogical demonstrations. Even 4 year-old children negatively evaluate teachers who leave out relevant information [@gweon2017order] or provide unnecessary information [@gweon2014children] with respect to a learner's goal or prior knowledge. Further, children adjust their exploratory behavior depending on whether an informant has previously provided complete information, suggesting that they are able to use others' history of informativeness to determine how much to trust current subsequent information.

Another possibility is that children might be biased to trust informants who always provide praise. Recent work has revealed that young children are biased to trust testimony from more positive sources, irrespective of the informativeness of the evaluation. Preschool children trust novel information from nicer informants [@johnston2015children], even when these informants lack expertise or perceptual access [@lane2013informants]. Young children are also more likely to endorse reliable speakers who make positive attributions [e.g., remarking that a character is "nice" versus "mean"; @boseovski2012trust] or positive evaluations of a student's product, independently of the speaker's competence in that domain [describing a painting @boseovski2017role]. However, in these studies, children did not have access to information about the target agent or agent's product so they were unable to evaluate whether the speaker's evaluation was appropriate or not. To the extent that children themselves can evaluate a product, they might be sensitive to the contingency of a speaker's evaluation on the subjective quality of the product and use this to judge the informational value of a speaker's praise.

Finally, children could be insensitive to the informativeness of others' praise. Children tend to hold strong beliefs about their own competence, which may interfere with their ability to integrate social information into their self-perceptions. Young children tend to overestimate their performance, predicting that they will perform better in the future than they are able to [@schneider1998performance], and judging that they have performed well when they have not [@hembacher2014don]. This positivity bias or “wishful thinking” towards their own abilities may undermine their ability to evaluate the informativity of feedback and use it to understand their own performance. [add final sentence here why we we think this is unlikely in this context?]

The present work asks whether young children can track the informativeness of others' praise by observing others' evaluations of another child, and if so, whether they can then use others' informativeness to appropriately evaluate their own work. We chose a task that preschool-aged children are familiar with but motivated to improve on: tracing shapes with a pen. Experiment 1 confirms that adults can differentiate between a teacher who always provides praise (Overpraise Teacher) and a  teacher who only praises the better tracings (Selective Teacher); they can use teachers' prior informativeness to appropriately evaluate which of two hidden tracings is better. In a similar, first-person paradigm, experiment 2 demonstrates that even 4- and 5-year-olds can differentiate between these two types of teachers and endorse the Selective Teacher's praise. Experiment 3 controls for the frequency of praise provided by each teacher by pitting the Selective Teacher against a teacher who only provides praise to the worse tracings (Selective-Reverse Teacher). 

```{r methods, fig.env = "figure*", fig.pos = "h", fig.align='center', fig.width=7, fig.height=7, set.cap.width=T, num.cols.cap=2, fig.cap = "(A) Examples of good and bad tracings that subjects saw in the warm-up evaluation questions and teacher videos for Experiments 1-3. (B) Teacher videos shown in Experiments 1-3. (C) Set-up and critical question for Experiments 2-3."}
img <- png::readPNG("figs/methods_final.png")
grid::grid.raster(img)
```

#Experiment 1: Adults

We began by investigating adults' ability to track different agents' histories of praise and make inferences about the informativeness of each agent's subsequent praise, as a baseline for estimating these capacities in young children. To this end, we had adult participants watch videos of two teachers giving feedback to the same child about tracings he had completed. One of the teachers gave selective praise, only praising the objectively good tracings, and the other teacher gave indiscriminate overpraise, praising both the good and bad tracings. We then asked participants to decide which of two unseen tracings was likely better, one praised by the teacher with a history of selective praise, or the one with a history of overpraise. 

We predicted that adults would treat praise from a teacher with a history of selective praise as more informative than praise from a teacher with a history of overpraise, and select the former tracing as more likely to be better. As an exploratory measure, we also asked adults which of these individuals was trying to be nice. We predicted that the agent providing overpraise would be perceived as trying to be nicer, although an agent providing more accurate feedback could also be perceived as more helpful, and therefore nicer.

##Methods

###Participants

```{r}
load("data/d_filt_adult.RData")

adult.dems <- d_filt_adult %>%
  ungroup() %>%
  mutate(gender = (gender == "female")) %>%
  summarise(n = n(),
            mean.age = mean(as.numeric(age)),
            sd.age = sd(as.numeric(age)),
            min.age = min(as.numeric(age)),
            max.age = max(as.numeric(age)),
            female_count = sum(gender))
```

`r adult.dems$n` adults (`r adult.dems$female_count` female, $M_{Age}$(SD) = `r round(adult.dems$mean.age, 2)` (`r round(adult.dems$sd.age, 2)`), range = `r adult.dems$min.age` - `r adult.dems$max.age`) were recruited from Amazon Mechanical Turk. An additional 14 subjects were recruited but excluded because they failed one or both memory check questions (see Procedures below).

###Stimuli 

Stimuli included images of tracings and videos of teacher-student interactions. Participants were shown two tracings to establish that they could accurately judge the quality of tracings in an initial evaluation question. One tracing was clearly good (i.e., the marker followed the template lines closely) and the other was clearly bad (Figure \ref{fig:methods}a). 

Participants also saw two videos in which a child received feedback about his tracings from different teachers (Figure \ref{fig:methods}b). In each video, the teacher ("Teacher Jane" or "Teacher Susan"; actor counterbalanced) was facing the camera on one side of the table and "Johnny", a child, was sitting with his back facing the camera. There were six tracings in a row on the table (three good tracings and three bad tracings, in alternating order). The good and bad tracings were equivalent in quality to the good and bad tracings shown in the initial evaluation question. 

At the start of the video, Johnny tells the teacher that he made the tracings and wants to know which tracings are good. Then, the teachers evaluate the tracings one at a time from right to left: in the Overpraise Teacher video, the teacher provides positive, undifferentiated feedback ("Wow, that's great!") for all six tracings and puts a colored star sticker on each tracing. The color of the star sticker matches the color of the teacher's shirt (red or green). In the Selective Teacher video, the teacher only provides positive feedback ("Wow, that's great!") and puts stickers on the good tracings. She gives neutral feedback ("Hm, this one's okay!") for the three bad tracings. Both teachers maintained a positive tone for both types of feedback.

###Procedure

Adults were first shown two tracings that differed in quality (see Stimuli section) and were asked to evaluate which of two tracings was better. Only participants who chose the better tracing were included in analyses. 

Next, participants were shown a picture of a child, Johnny, and were told that he wanted to know which of his tracings were good because he was going to enter one of them into a contest. Then, participants watched videos of the Selective Teacher and Overpraise Teacher (video order counterbalanced). After each video, as a memory check, participants were asked how many tracings the teacher said were great. Only subjects who answered this correctly ("3" for the Selective Teacher and "6" for the Overpraise Teacher) were included in analyses. 

After watching the videos, participants were shown a picture of Kristen, another student who was working on two tracings and also wanted to enter one of them into a contest. They were shown two envelopes and told that each envelope contained one of Kristen's drawings. Participants were told that the Selective Teacher saw only one of the tracings and praised it (e.g., "Teacher Jane said this tracing is great"), and the Overpraise Teacher saw only the other tracing and praised it ("Teacher Susan said this tracing is great"). Participants never saw Kristen's actually tracings, only the envelopes with the corresponding stickers on them.

Finally, participants were asked the critical question: "Now Kristen is going to bring one of her tracings to a contest. Which tracing should she bring?" Then, as an exploratory measure, participants were asked  "One of the teachers wanted to be nice. Who was trying to be nice?" 

##Results and Discussion

```{r}
#Make tables for adult data
adult.tracing <- d_filt_adult %>%
  group_by(condition) %>%
  multi_boot_standard(col = "tracing_choseContingent") %>%
  mutate(question = "Better tracing?") %>%
  mutate(age_bin = "Adults")

adult.nicer <- d_filt_adult %>%
  group_by(condition) %>%
  multi_boot_standard(col = "nicer_choseContingent") %>%
  mutate(question = "Nicer teacher?")

adult.table = full_join(adult.tracing, adult.nicer)
```

```{r}
#results plot
load("data/d_filt_e2.RData")
load("data/d_filt_e3.RData")

e1_data_plot <- d_filt_adult %>%
  transmute(id = id,
            tracing_selective = tracing_choseContingent,
            experiment = "E1: Adults")
  
e2_data_plot <- d_filt_e2 %>%
  transmute(id = sid,
            tracing_selective = tracing_selective,
            experiment = "E2: 4 & 5 yrs")

e3_data_plot <- d_filt_e3 %>%
  transmute(id = sid,
            tracing_selective = tracing_selective,
            experiment = "E3: 4 yrs")

full_data <- bind_rows(e1_data_plot, e2_data_plot)%>%
  bind_rows(e3_data_plot)

full_data_plot <- full_data %>%
  group_by(experiment) %>%
  multi_boot_standard(col = "tracing_selective")
```

```{r results, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=7.5, fig.height=5, out.width="3in", out.height="2in", set.cap.width=T, num.cols.cap=1, fig.cap = 'Results of Experiments 1-3: Proportion of participants choosing the tracing praised by the selective praiser. In Experiments 1 and 2, participants chose between Selective and Overpraise Teachers, and in Experiment 3, participants chose between Selective and Selective-Reversed Teachers. Error bars are 95 percent confidence intervals.'}

# ggplot(full_data_plot, aes(x = experiment, y = mean, fill = experiment)) +
#   geom_bar(stat="identity", width=.5) +
#   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),
#              position = position_dodge(width = .5))+
#   ylab("Tracing Praised by Selective Praiser") +
#   scale_fill_viridis(discrete = TRUE) +   
#   ggthemes::theme_few() + 
#   ylim(0,1) +
#   ggtitle("Which tracing is better?")+ 
#   theme(axis.title.x=element_blank(),
#         title = element_text(vjust=0.5, size=22),
#         legend.position="none",
#         axis.text.x  = element_text(vjust=0.5, size=20),
#         axis.text.y  = element_text(vjust=0.5, size=20),
#         axis.title.y = element_text(size=20))

ggplot(full_data_plot, aes(x = experiment, y = mean, fill = experiment)) +
  geom_bar(stat="identity", width=.5) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),
             position = position_dodge(width = .5))+
  ylab("Tracing Praised by Selective Praiser") +
  scale_fill_viridis(discrete = TRUE) +   
  ggthemes::theme_few() + 
  ylim(0,1) +
 # ggtitle("Which tracing is better?")+ 
  theme(axis.title.x=element_blank(),
        title = element_text(vjust=0.5, size=22),
        legend.position="none",
        axis.text.x  = element_text(vjust=0.5, size=20),
        axis.text.y  = element_text(vjust=0.5, size=20),
        axis.title.y = element_text(size=20))
```

```{r}
#Analyze adult data
adult.n = d_filt_adult %>%
  summarise(tracing.n = sum(tracing_choseContingent), # number of subjects who chose the tracing praised by the Selective Teacher
            nicer.n = sum(nicer_choseContingent), # number of subjects who chose the Selective Teacher as trying to be nice
            total.n = n())

#Tracing question
adult.binom.tracing <- binom.test(adult.n$tracing.n,adult.n$total.n)

#Nicer question
adult.binom.nicer <- binom.test(adult.n$nicer.n, adult.n$total.n)

e1.plot = ggplot(adult.table, aes(question, mean, fill = question)) +
  geom_bar(stat = "identity", width = .5) +
  ylim(0,1) +
  ggtitle("Experiment 1: Adults") +
  theme(plot.title = element_text(hjust=0.5, size=12),
        text = element_text(size=12),
        axis.title.x=element_blank()) +
  guides(fill=FALSE) + 
  geom_linerange(data = adult.table, mapping=aes(x=question, ymin = ci_lower, ymax=ci_upper))+
  geom_hline(yintercept=.5, linetype="dotted") +
  ggthemes::theme_few() +
  langcog::scale_colour_solarized() +
  labs(x = "Question", y = "Proportion Choosing Contingent Praiser")
```

<!-- Mika -- need to check order of teachers and actor type for any effect.. -->
Our primary question was whether adults use teachers' prior patterns of praise to evaluate the informativeness of subsequent praise. Although each teacher provided identical evaluations of the tracings, subjects overwhelmingly chose the tracing praised by the Selective Teacher (`r round(adult.table$mean[1]*100,2)`\%, $p$ < .001, Binomial Test; Figure \ref{fig:results}). Further, subjects agreed that the Overpraise Teacher was *trying* to be nice (`r 100-(round(adult.table$mean[2]*100, 2))`\%, $p$ < .001, Binomial Test), suggesting that adults infer niceness as a communicative goal from this pattern of undifferentiated praise. These results confirm our prediction that adults are sensitive to the informativeness of others' feedback: given observations of others' prior feedback, they can evaluate the differential informativeness of subsequent feedback and use it to judge the likely quality of an unseen product. 

#Experiment 2

Experiment 2 was designed to assess whether preschool-aged children can also assess the informativeness of praise based on individuals' histories of praise. The design was similar to Experiment 1, except that children themselves completed two tracings. They then watched the same videos as in Experiment 1. Children were then told that one of their own tracings had been praised by the Selective Teacher, and one had been praised by the Overpraise Teacher. Children were asked to decide which of their tracings was better based on the feedback from the teachers. We predicted that if children were sensitive to the informativeness of praise based on each teacher's history, children should weight the Selective Teacher's praise more heavily, and select the tracing praised by her. On the other hand, if children prefer to accept information from agents they perceive as positive or friendly, they might prefer the Overpraise Teacher. Finally, if children are not sensitive to the relative informativness of praise, they might choose a tracing at random. Similar to Experiment 1, we also assessed which teacher children thought was trying to be nicer.

```{r}
load("data/d_filt_e2.RData")

e2.dems <- d_filt_e2 %>%
  ungroup() %>%
  mutate(gender = (gender == "f")) %>%
  summarise(n = n(),
            mean.age = mean(as.numeric(age)),
            sd.age = sd(as.numeric(age)),
            min.age = min(as.numeric(age)),
            max.age = max(as.numeric(age)),
            female_count = sum(gender))
```

##Methods

### Participants
`r e2.dems$n` four- and five-year-olds (`r e2.dems$female_count` female, $M_{Age}$(SD) = `r round(e2.dems$mean.age,2)`(`r round(e2.dems$sd.age,2)`), range = `r round(e2.dems$min.age,2)` - `r round(e2.dems$max.age,2)`) were recruited from a local preschool^[Planned sample size, exclusion criteria, and analysis plan preregistered at https://aspredicted.org/4r9dh.pdf]. An additional 5 subjects were tested but excluded due to failure on one or two memory check questions or a warm-up question (see Procedures below).

<!-- check exclusions -->

### Stimuli

Stimuli were the same as those from Experiment 1, except that children also traced two templates (each had a circle and either an overlapping triangle or square) on an 8.5 x 11'' sheet of paper with a thick blue marker (Figure \ref{fig:methods}b). The tracings that children evaluated during the warm-up phase, as well as pictures of the teachers (Susan and Jane) and the student (Johnny) were presented on laminated sheets of paper. Children were shown the videos on a 13" Macbook Pro laptop. 

### Procedure
Children were tested in a private room inside of the preschool. The experimenter first told children that the goal of tracing was to stay as close to the lines as possible and demonstrated tracing a rectangle for the child. Then, the child traced the two templates, and the experimenter put each tracing away into a manila envelope so the child could not see the tracing for the remainder of the session.

<!-- Warm up evaluation questions -->
Next, children were asked to evaluate two pairs of tracings to verify that they could tell the difference between good and bad tracings. As in Experiment 1, in each pair, one tracing was obviously good and the other tracing was obviously bad. Children were asked to judge which tracing was better; only children who chose the better tracing in each pair were included in analyses. 

<!-- Introduction to Johnny and teacher videos -->
Children were then shown a picture of a student, Johnny. The experimenter told children that Johnny was working on his tracings earlier and wanted help figuring out which of his tracings were good because he wanted to show them to his class later. Children watched the same Selective Teacher and Overpraise videos as in Experiment 1. After each video, to verify that children understood and remembered each teacher's pattern of praise, children were shown a still frame of the video (with no stars on the drawings) and were asked which tracings the teacher said were great. Children responded by pointing to the tracings. If children incorrectly pointed to a tracing or missed a tracing, then the video was replayed and the memory check question was asked again. Only children who passed the memory check question by the second attempt were included in analyses. 

<!-- % Test question -->
After children watched the videos of the teachers and responded to the memory checks, the experimenter told the child that Teacher Jane and Teacher Susan were close by and they could give feedback on the subject's tracings from earlier. The experimenter left the room for 15 seconds with the envelopes containing the child's tracings and then returned. The experimenter said "Teacher Jane looked at this tracing and said that this one is great" (pointing to one of the envelopes, and placing a photo of Teacher Jane beside it) and "Teacher Susan looked at this tracing and said that this one is great" (pointing to the other envelope and placing a photo of Teacher Susan beside it). Each envelope also had the corresponding teacher's sticker on it. Finally, with the tracings still in the envelopes, the experimenter asked the child the critical question: "Now you can bring back your best tracing to show your teacher! Which one do you think is the best?" Children responded by pointing to one of the envelopes. As an exploratory measure, children were then asked, "Which teacher do you think was trying to be nicer?" Children responded by pointing to one of the photos of the teachers.

```{r}
#get means and CIs for plots

e2.tracing <- d_filt_e2 %>%
  group_by(include) %>%
  multi_boot_standard(col = "tracing_selective") %>%
  mutate(question = "Better tracing?")

e2.nicer <- d_filt_e2 %>%
  group_by(include) %>%
  multi_boot_standard(col = "nice_selective") %>%
  mutate(question = "Nicer teacher?")

e2.table = full_join(e2.tracing, e2.nicer)

e2.plot = ggplot(e2.table, aes(question, mean, fill = question)) +
  geom_bar(stat = "identity", width = .5) +
  ylim(0,1) +
  ggtitle("Experiment 2: 4-5 year-olds") +
  theme(plot.title = element_text(hjust=0.5, size=12),
        text = element_text(size=12),
        axis.title.x=element_blank()) +
  guides(fill=FALSE) + 
  geom_linerange(data = e2.table, mapping=aes(x=question, ymin = ci_lower, ymax=ci_upper))+
  geom_hline(yintercept=.5, linetype="dotted") +
  ggthemes::theme_few() +
  langcog::scale_colour_solarized() +
  labs(x = "Question", y = "Proportion Choosing Contingent Praiser")
```

```{r}
contest_n = d_filt_e2 %>%
  summarise(selective_n = sum(tracing_selective),
            total_n = n())

binom_contest <- binom.test(contest_n$selective_n[1],contest_n$total_n[1])
```

```{r}
#logistic regression
#trimmed condition because model would not converge
e2_agereg = summary(glmer(tracing_selective ~ age  +
               (1|sid), 
               data = d_filt_e2, 
               family = "binomial"))
```

##Results and Discussion

Our main question was which tracing children thought was better: the tracing praised by the Overpraise Teacher or the tracing praised by the Selective Teacher. Since children could not see which of their tracings was in each envelope, the teachers' praise was the only criteria available to children to evaluate which of their tracings was better. Only children who passed the initial evaluation questions and the memory check questions for each teacher video by the second attempt were included in the following analyses.

We found that children were significantly more likely to choose the drawing that had been praised by the Selective Teacher (`r round(e2.table$mean[1]*100,2)`\%, $p$ = `r round(binom_contest$p.value,3)`; Binomial Test). To investigate whether children's age predicted their choice, a logistic regression was fit with the following structure: `Tracing choice ~ Age in Months + (1 | Subject)`. Children's age did not predict their choice of tracing ($B$ = `r round(e2_agereg$coefficients[2],2)`, $z$ = `r round(e2_agereg$coefficients[6],2)`, $p$ = `r round(e2_agereg$coefficients[8],2)`).

Thus, even preschool-aged children appear to be sensitive to the informativity of praise based on whether the agent has a history of contingent praise or not. Importantly, this means that the majority of children were able to override any positivity bias and avoid selecting the drawing associated with the Overpraise teacher, who might have been perceived as more nice or likeable.

Notably, in this experiment, teachers patterns' of praise differed in two important ways. First, they differed in the *selectivity* of tracings praised — the Contingent teacher praised only three out of the six tracings present, while the Selective teacher praised all six. Secondly, they differed in their contingency on *quality* — the Selective Teacher only praised tracings that were objectively better, while the Overpraise teacher praised all tracings independent of quality. Thus, it is unclear whether children treated the Selective Teacher's praise as more informative because she previously only praised good tracings, or merely because she was previously selective. We addressed this question in Experiment 3.

#Experiment 3

In Experiment 3, we asked whether children give more weight to praise from individuals who give selective praise that is matched with quality compared to individuals who give selective praise that is mis-matched with quality. Children observed videos similar to those in Experiments 1 and 2, except that one teacher praised only the good tracings (identical to the Selective Teacher in Experiments 1 and 2) and the other teacher praised only the bad tracings (Selective-Reverse Teacher). We predicted that if children track the correspondence between praise and quality, and not merely selectivity, they should believe a tracing praised by the Selective Teacher is likely to be better than one praised by the Selective-Reverse Teacher.

##Methods

###Participants

```{r}
load("data/d_filt_e3.RData")

e3.dems <- d_filt_e3 %>% 
  ungroup() %>%
  mutate(gender = (gender == "f")) %>%
  summarise(n = n(),
            mean.age = mean(as.numeric(age)),
            sd.age = sd(as.numeric(age)),
            min.age = min(as.numeric(age)),
            max.age = max(as.numeric(age)),
            female_count = sum(gender))
```

`r e3.dems$n` 4-year-olds (`r e3.dems$female_count` female, $M_{Age}$(SD) = `r round(e3.dems$mean.age,2)`(`r round(e3.dems$sd.age,2)`), range = `r round(e3.dems$min.age,2)` - `r round(e3.dems$max.age,2)`) were recruited from a local preschool. An additional XX subjects were tested but excluded due to failure on one or two memory check questions or a warm-up question.

###Stimuli and Design

Stimuli were identical to Experiment 2 except the Overpraise Teacher's video was replaced with the Selective-Reverse Teacher's video. The Selective-Reverse Teacher's video was identical to the Selective Teacher's video, but the teacher praised and gave stars only to the bad tracings and provided a neutral response to the good tracings. 

###Procedure

The procedure was identical to Experiment 2. As in Experiment 2, the order of the videos and the actor playing each type of teacher was counterbalanced.

##Results and Discussion

```{r}
e3.tracing <- d_filt_e3 %>%
  group_by(include) %>%
  multi_boot_standard(col = "tracing_selective") %>%
  mutate(question = "Better tracing?")

e3.nicer <- d_filt_e3 %>%
  group_by(include) %>%
  multi_boot_standard(col = "nice_selective") %>%
  mutate(question = "Nicer teacher?")

e3.table = full_join(e3.tracing, e3.nicer)

e3.plot = ggplot(e3.table, aes(question, mean, fill = question)) +
  geom_bar(stat = "identity", width = .5) +
  ylim(0,1) +
  ggtitle("Experiment 3: 4 year-olds") +
  theme(plot.title = element_text(hjust=0.5, size=12),
        text = element_text(size=12),
        axis.title.x=element_blank()) +
  guides(fill=FALSE) + 
  geom_linerange(data = e3.table, mapping=aes(x=question, ymin = ci_lower, ymax=ci_upper))+
  geom_hline(yintercept=.5, linetype="dotted") +
  ggthemes::theme_few() +
  langcog::scale_colour_solarized() +
  scale_fill_grey() +
  labs(x = "Question", y = "Proportion Choosing Contingent Praiser")
```

```{r eval = FALSE}
r results_adult, fig.env='figure*', fig.align='center',fig.width=7,fig.height=3, fig.pos='h',num.cols.cap=1, fig.cap='Results of Experiment 1, 2, and 3.'}
img <- png::readPNG("figs/fig2_color.png")
grid::grid.raster(img)
```

```{r}
tracing_n = d_filt_e3 %>%
  summarise(selective_n = sum(tracing_selective),
            total_n = n())

binom_tracing <- binom.test(tracing_n$selective_n[1],tracing_n$total_n[1])
```

```{r}
#logistic regression
#trimmed condition because model would not converge
e3_agereg = summary(glmer(tracing_selective ~ age  +
               (1|sid), 
               data = d_filt_e3, 
               family = "binomial"))
```

Our main question was whether children track the contingency of praise with quality and use this to infer the informativeness of subsequent praise, or whether they treat all selective praise the same regardless of its contingency with quality. We found that children <!-- add results here ---> (`r round(e3.table$mean[1]*100,2)`\%, $p$ = `r round(binom_tracing$p.value,2)`; Binomial Test). As in Experiment 2, to investigate whether children's age predicted their choice, a logistic regression was fit with the following structure: `Tracing choice ~ Age in Months + (1 | Subject)`. Children's age did <!-- add results here ---> not predict their choice of tracing ($B$ = `r round(e3_agereg$coefficients[2],2)`, $z$ = `r round(e3_agereg$coefficients[6],2)`, $p$ = `r round(e3_agereg$coefficients[8],2)`).

# General Discussion

<!-- Finally, children could be insensitive to the informativeness of others' praise. Children tend to hold strong beliefs about their own competence, which may interfere with their ability to integrate social information into their self-perceptions. Young children tend to overestimate their performance, predicting that they will perform better in the future than they are able to [@schneider1998performance], and judging that they have performed well when they have not [@hembacher2014don]. This positivity bias or “wishful thinking” towards their own abilities may undermine their ability to evaluate the informativity of feedback and use it to understand their own performance. -->


In three experiments, we examined how children and adults evaluate the informativeness of others' praise and use it to determine the quality of their own or others' work. Experiment 1 confirms that adults differentiate between a teacher who \textit{always} provides praise irrespective of the quality of the product and a teacher who provides praise contingent on the quality. Experiment 2 shows that 4-5 year-old children distinguish between these patterns of praise and weigh the Contingent Teacher's feedback more heavily in deciding which of their two tracings is better. Experiment 3 shows that when the amount of praise and contents of evaluation are held constant, 4 year-olds prefer evaluations from teachers who provide more accurate evaluations. These findings suggest that young children spontaneously evaluate the informativeness of others’ praise based on the contingency between praise and quality, and that when assessing their own work, children give more weight to praise from informative teachers.

<!-- Should note here that the effect (in experiment 2 at least) is relatively small- children are nowhere near ceiling at selecting the Accurate teacher. So there is obviously some development that happens, which can be investigated in future research. -->

Children's preference for the Selective Teacher is relatively weak compared with adults' preference. There are a few possible explanations for this discrepancy: (1) young children have relatively minimal experience evaluating products they have created, (2) they also have minimal experience in receiving neutral or negative feedback so they might have difficulty reasoning about its informational value, and (3) they might have a more difficult time inhibiting a desire to interact or agree with positively valenced agents. Since children gain more experience with receiving performance feedback and evaluating their own work in elementary school, older children may show a stronger preference for learning from teachers who provide accurate, contingent praise.

In this study, we intentionally provided a \textit{contrast} between two teachers who vary in their informativeness and accuracy. However, when learning novel words, preschool-aged children have been observed to trust even inaccurate, unreliable informants in the absence of an accurate or informative adult [@jaswal2010young, @vanderbilt2014absence]. Recent work has suggested that young children need access to relevant alternatives to compute pragmatic implicatures [@barner2011accessing, @skordos2016children] or evaluate the informativeness of pedagogical demonstrations [@gweon2017order]. Thus, without the alternative of an accurate, contingent praiser, young children might be willing to trust a teacher who provides inaccurate or overpraise.  It might be important for young children to witness multiple informants to most effectively evaluate them (by better understanding what the teachers \textit{could} have said); future work should explore these possibilities. 

Further, children were asked to evaluate two tracings endorsed by each teacher. One open question is whether young children might differentially weight praise based on their own goals in relation to the task. Here, the learner's goal in the video demonstration ("Johnny wants help figuring out which tracings are good because he wants to show them to his class later") and the subject's goal ("Now you can bring back your best tracing to show your teacher") was made explicit by the experimenter. However, learners may have diverse goals in approaching adults or teachers for help -- they could want honest evaluations of the quality of their work and suggestions on how to improve, or they might seek affirmation of their efforts and attempts without any evaluations on the work, and so on. 

These goals could depend on children's sense of their competence in a task or domain; children who are just learning a new task might want more affirmation and positivity while children who are fine-tuning their abilities might want more constructive feedback. Children’s need for accurate feedback might also depend on their interpretation of the activity; if they perceive the activity to be just for fun, it may not be important to get accurate feedback, but if they believe the objective quality of their work matters, for example, because it will be entered in a contest or receive a grade, they might place more weight on informative feedback. Future research that manipulates children’s task-related goals will be needed to address these possibilities.

<!-- When evaluating their tracings in this task, children did not have visual access to each tracing, so they could only use the teacher's evaluation and prior observations of the teacher to make the judgment. How do children integrate their own beliefs about the quality of a piece of work with a teacher's evaluation? One possibility is that children might put more weight on their own beliefs when they are more certain about how well they are doing; this certainty could rely jointly on task characteristics (e.g., the product having an objective measure for quality such that the "true" state is more obvious) and the child’s metacognitive awareness of their own skill or performance in the given domain. -->

When evaluating their tracings in this task, children did not have visual access to each tracing, so they could only use the teacher's evaluation and prior observations of the teacher to make the judgment. How do children integrate their own beliefs about the quality of a piece of work with a teacher's evaluation? One possibility is that children might put more weight on their own beliefs when they are more certain about how well they are doing; this certainty could rely jointly on task characteristics (e.g., the product having an objective measure for quality such that the "true" state is more obvious) and the child’s metacognitive awareness of their own skill or performance in the given domain. Furthermore, we plan to investigate how others' feedback might differentially influence not only product evaluations but also subsequent learning efforts and persistence on various tasks. Recent work has shown that infants' and young children’s observations of others' attempts influences their effort and persistence [@leonard2017infants, @magid2015quit].

Overall, the present work demonstrates that young children monitor the contingency of others’ praise with the quality of the work they are evaluating, and use this information to interpret the informational value of subsequent praise. This is likely a critical skill, as both children and adults constantly receive praise that might be motivated by different goals and levels of competence. Accurately representing the informational value of this praise should allow children to gain insights into their personal strengths and weaknesses and guide their learning accordingly. 

# Acknowledgements

We thank Molly Irvin for her assistance with data collection, and Athena Braun, Fernanda Kramer, and Johnny Matheou for their help in stimuli creation. We also thank the parents and families of Bing Nursery School for their support. This work was supported by an NSFGRFP to MA, [] to EH, and Stanford Psych-Summer funding to HQ and BA.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
